|

### 2022-11-29 response-reviewers/response-reviewers.tex

\documentclass[a4paper,12pt]{article}
\usepackage{anysize}
\usepackage[T1]{fontenc}
\usepackage[stable]{footmisc}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=0.825]{FiraMono}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{mathtools}
\usepackage[authoryear]{natbib}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{babelbib}
\usepackage{graphicx}
\usepackage{booktabs, makecell, longtable}
\usepackage{dcolumn}
\usepackage{float}
\usepackage[caption = false]{subfig}
\floatplacement{figure}{H}
\usepackage{caption}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcomman{\elandscape}{\end{landscape}}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{markdown}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\setcitestyle{aysep={}}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
   {\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\usepackage{hyperref}

\hypersetup{
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true}

\newcommand*\justify{%
  \fontdimen2\font=0.4em% interword space
  \fontdimen3\font=0.2em% interword stretch
  \fontdimen4\font=0.1em% interword shrink
  \fontdimen7\font=0.1em% extra space
  \hyphenchar\font=`\-% allowing hyphenation
}

\begin{document}

\doublespacing

\noindent \textbf{Research \& Politics}

\noindent \today

\vspace{.5cm}

\noindent Dear Editor and Reviewers,

\vspace{.5cm}

We would like to thank you for the opportunity to revise our manuscript,
``Vigilantism and Institutions: Understanding Attitudes toward Lynching in
Brazil'' (Ms. No. RAP-22-0164). Following the comments and suggestions of the
editors and reviewers, we have thoroughly revised our research letter and we
believe it has improved significantly as a result.

We were especially committed to increasing the appeal of our research note to BJPolS's readership, emphasising the dialogue between our findings and those in the literature. We did this by extensively editing the Introduction and Discussion sections. We expand the literature review and add more references to the original theory as recommended by the editor and Reviewers 1 \& 2. We detail how the latest papers on the relationship between legislative size and public expenditure frame that debate and attempt to resolve it. We have also moved the references to our methodology from the Introduction to the Data and Methods section, as per the suggestion of Reviewer 2, to dedicate more space to theoretical issues. In the Discussion, having presented our results, we further specify the reasons why we believe past results have been highly heterogeneous. Lastly, we recommend possible avenues for further research that follow from our analyses, such as testing combinations of variables that we did not find in our search or measuring how domestic factors like gerrymandering or party effects influence the dynamics of the "law of $1/n$".

Following Reviewer 3's proposition, we conducted two new paper searches to broaden the scope of our previous query. In the first search, we ran a keyword-based query on Google Search to look for articles that discuss the "law of $1/n$" but do not cite \citet{weingast1981political}. We also checked the personal websites of the authors we had previously included in the paper in order to find unpublished research on our topic of interest. We thank Reviewer 3 for their insightful comment, as we included 2 new articles in our analysis as a result.

Throughout the paper, we clarify all of Reviewer 1 \& 2's questions about our independent variables, coding procedures, and modelling techniques. We have also changed our model specifications to more properly account for effect size independence, following Reviewer 2's critique. We identified the sources of dependence in our sample and adopted multilevel random effects models in all of our estimations. We are extremely appreciative of this recommendation, as it is now an important methodological strength in our paper.

When it comes to our results, we follow Reviewer 2's insight on how to interpret the evolution of research designs, toning down the idea that most of the variation in our estimates derives from methodological choices. We also present new results by adding a moderator for unicameralism, following Reviewer 1's reference.

Below we discuss these changes in further detail, as well as the other
improvements we have done to the paper in response to the editors' and
reviewers' comments. We are pleased with the outcome and hope to have satisfied
all of your concerns. Again, we thank the editor for the opportunity to revise
our manuscript, and the reviewers for their immensely valuable comments.

\vspace{.5cm}

\noindent Yours Truly,

\vspace{.5cm}

\noindent The Authors

\section*{Editor Comments and Responses}

\textbf{1)} The editor writes: ``The Reviewers provide helpful comments. Specifically, Reviewer 1 suggests that you re-frame the paper to acknowledge that the inconsistency of the results has long been understood in the literature, and that the search for explanations of that inconsistency is an important driver of that literature. Please give further thought to the key contribution of your meta-analysis against that background, as Reviewers 1 and 2 suggest, and discuss the theoretical contribution and its meaning more fully in the introduction and conclusion.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have completely restructured the Introduction and Discussion sections to establish a better dialogue with the literature. We better contextualise our motivation to write this piece and more concretely demonstrate the implications of our results regarding previous findings. To illustrate the theory, we have provided the reader with a brief summary of the "law of $1/n$" model in Section A of the Supplementary Materials. We have also expanded the literature review in the Introduction. In the Discussion section, our hypotheses on the sources of heterogeneity are more clearly connected with the themes previously explored in the literature.

    We refer to these changes more specifically in our responses to Reviewer 1 in page 3, and to Reviewer 2 in page 7 of this document.
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} The editor writes: ``All Reviewers also provide detailed comments on your empirical analysis. Reviewer 3 has useful suggestions regarding your sampling strategy; Reviewers 1 and 2 focus on your dependent and explanatory variable. Please address these comments.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have followed Reviewer 3's suggestion and nearly tripled the amount of records we assessed for eligibility, seeking articles within the distributive politics literature through broader criteria. Thanks to this review, we added two new articles to our meta-analysis.

    The main methodological adaptation we made was in response to Reviewer 2's extremely valuable comment on the need for using multilevel models. We are extremely grateful for this comment, and we thank Reviewer 2 for pointing out this crucial aspect in our empirical strategy.

    We also added a series of clarifications regarding our coding procedures, specially regarding the independent variables. We specify where these explanations can be found in the main article along this letter, according to each of the specific suggestions the Reviewers made.
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} The editor writes: ``Reviewers 1 and 2 also ask you to make better use of the Supplementary Materials (SI). In your main text, please refer to specific sections in the SI, please explain your results in the SI, and leave out the R code, which should be made publicly available separately from the SI with the replication materials.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have made the changes requested by Reviewers 1 and 2 accordingly. The ``Supplementary Materials'' we refer to hereinafter contain only a discussion of the \citet{weingast1981political} and \citet{primo2008distributive} models in Section A, a detailed description of the search and eligibility procedures for study inclusion (Sections B and C), a guide to how we built the meta-analysis dataset from our pool of diverse coefficients (Section D), a presentation of the descriptive statistics of the included articles (Sections E and F), and the results for the binomials tests, meta-analyses, and meta-regressions (Sections G through K). The R scripts we previously presented along with this information are now in a different document referred to as ``Replication Materials''. For the purpose of reproducibility, the full datasets listing all the records we assessed and the stage and reason for each exclusion are also available online for consultation in the article's GitHub repository. 
\end{quote}

\vspace{.3cm}

We would like to thank the editors for their helpful comments and suggestions.

\section*{Reviewer 1 Comments and Responses}

\noindent \textbf{1)} Reviewer 1 writes: ``It has long been known that the empirical results are inconsistent in this literature. To wit, a major theme in the empirical literature -- at least for the last decade or so -- has been to try to explain the previously inconsistent findings, especially between upper and lower chambers; papers like Chen and Malhotra, Crowley, Lee, etc. take it as a main motivation to explain these inconsistencies. There have also been theoretical contributions in this vein, such as Pecorino's 2018 piece in Public Choice. In other words, these various approaches the authors note have been evolving not just as new techniques have been made available, but precisely *because* of the inconsistency in the findings the authors are discussing here. While I understand this paper is endeavoring to be concise, some service should be paid to a fuller discussion of the trends in the literature--noting that the previous authors in this literature were well aware of its inconsistent results--beyond just changes in methodology.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Reviewer 1 makes an excellent point. We agree that we had not properly expressed how more recent works identified and searched for strategies that solved the discrepancies in the literature. We have changed the framing of the paper so it is clear that scholars were well aware of the heterogeneity, and that our contribution in this sense is to quantitatively find the sources of such variation. While this idea permeates the Introduction section, here is one sentence we added that specifically addresses this point (p.2):

    ``\textit{In this respect, scholars have long been aware of the theoretical and empirical limitations of the ``law of $1/n$'', and the proliferation of new studies reflect a conscious attempt to assess the robustness of the theory.}''

    As mentioned above, we have also expanded the literature review from paragraphs 1 through 3 in the Introduction section (p.2) as follows:

    ``\textit{Early studies that empirically tested the "law of $1/n$", as the theory is currently known, indeed found a positive correlation between the number of legislature seats and different measures of government spending, although these first results were mainly based on US state legislatures and the effect was often limited to one house (e.g., \citet{baqir2002districting, gilligan1995deviations, gilligan2001fiscal}).}

    \textit{Later research, however, has questioned the validity of the "law of $1/n$". \citet{primo2008distributive} affirm that, due to spatial spillovers, a collection of small districts can supply public goods more efficiently than the central government. The authors conclude that a "reverse law of $1/n$" may hold, wherein a higher number of legislators in small constituencies decrease the overall public spending. Similarly, \citet{primo2006stop} and \citet{chen2007law} find that lower and upper chambers may have mixed effects on government spending, while \citet{petterssonlidbom2012size} argues that the impact of larger chamber sizes is negative when using data from Finland and Sweden.}

    \textit{Since many empirical tests of the "law of $1/n$" have produced conflicting results, scholars have expanded this research agenda and closely investigated how institutional factors condition the original formulation of the theory. For instance, authors such as \citet{crowley2019law} and \citet{pecorino2018supermajority} accurately point out that collective action problems have been overlooked in the literature, and recent findings indicate that bicameralism \citep{maldonado2013legislatures}, intergovernmental competition \citep{crowley2015local}, redistricting \citep{lee2018court}, and party ideology \citep{bjedov2014impact} strongly influence the relationship between seats and spending. Moreover, the literature has increasingly applied causal inference methods to estimate the effect of the "law of $1/n$", and in contrast to previous studies using panel data, regression discontinuity designs generally indicate that more legislators decrease public expenditures \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 1 writes: ``In the empirical exercise, the authors routinely reference separating the empirical studies they use as their sample based on the "main explanatory variable." For instance, in section 3.3. This strikes me as problematic (or at least poorly explained) because it is typically standard in this literature (at least for those studies on bicameral legislatures such as cross-state studies on the US) to include both the upper and lower chamber size variables. So it is unclear to me how such a study would have a "main explanatory variable." This needs to be more clearly explained.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that our explanations regarding the choice and use of the variables of interest were insufficient. When studies use evidence from bicameral legislatures, we included the coefficients for both upper and lower chamber size in all our samples. This is the case for thirteen articles in our analysis. Using data from both chambers is one of the reasons why our restricted sample contains 45 coefficients for a total of 30 papers. We added clarifications regarding our choice of independent variable in the first paragraph of the Data and Methods section, on page four.

    A specific comment on variable choice in bicameral systems is in footnote \#2. It reads: ``\textit{Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as main explanatory variables.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 1 writes: ``In Table 3, the authors also only present N and log(N) results; K is not indicated—was it an excluded group? If so, this needs to be made clear.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We acknowledge that Table 3 did not display the reference categories clearly enough. We have highlighted the notes below the table so the reader can have a more straightforward interpretation of the estimates. They present the reference category for each variable and moderator in the meta-regressions. For the independent variable, the reference category was upper chamber size, which is why this category was omitted in the table.
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 1 writes: ``Further, it is not clear to the reader why the authors use lower chamber size, upper chamber size, and then a log of only lower chamber size. Are there no studies which employ a log of upper chamber size?''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Following the reviewer's remark, we double checked our study sample and confirm that the natural logarithm of upper chamber size is not present in any papers. As mentioned above, we included clarifications about our choice of independent variable in the first paragraph of the Data and Methods section (p.4). Footnote \#2 reads: ``\textit{We did not find any article that used the natural logarithm of upper chamber size in their models.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 1 writes: ``How did the authors handle those studies in this literature which focused on unicameral legislatures? Were these grouped in with the "lower chamber" studies? Were they excluded? This is not clearly explained in the paper. In general, the results on unicameral legislatures tend to support the law of $1/n$.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As noted above, we agree that important details about data collection and coding were missing. Unicameral legislature sizes were coded under lower chamber size or natural logarithm of lower chamber size. Many studies consider lower chambers and unicameral legislatures as analogous institutions for quantitative purposes. An example is one of the papers in our meta-analysis \citep{stein1998institutional}. We expand the explanations surrounding the treatment of independent variables in the first paragraph of the Data and Methods section. A specific clarification on unicameral legislatures is in Footnote \#2. It reads: ``\textit{There are a few important nuances concerning coding of these variables. Unicameralism, for example, is captured both by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).}''

    Upon reading this comment, we also acknowledged that although the differences between upper and lower chambers were so relevant to the discussion, we had not given enough attention to unicameral legislatures. Inspired by this remark, we coded a new moderator for institutional design. The categories were `Unicameral', for coefficients from purely unicameral systems; `Bicameral', for coefficients from purely bicameral systems; and `Mixed', for coefficients from studies that used samples which contained a mix of unicameral and bicameral systems. Examples of the latter were all the papers that used country-level data. Our findings confirm the Reviewer's insight: in the meta-regressions that aggregate all coefficients, unicameralism is a significant positive predictor of the $1/n$ effect.

    Since this is an important finding, we discuss the Institutional Design moderator in all sections. The Data and Methods section presents under which category each article fits in Table 1, and its descriptive statistics in Table 2. In the first paragraph of the Meta-Regressions subsection, we explain how the variable is coded (p.12), and briefly interpret its results in the last paragraph (p.14).

    Because we found such interesting results in the meta-regressions, we decided to perform subgroup analyses with heterogeneous effects for unicameralism as well. The results can be found in section H.13 in the Supplementary Materials. We undertook tests similar to those we present in the article for Estimation Methods (p.12). Using the lower chamber size $\times$ per capita expenditure combination, we aggregated the data in two groups: one just for unicameral systems, and the other for all institutional designs excluding unicameralism. For unicameral systems, the estimates were mostly positive in the restricted sample, but none was statistically significant. Results were overwhelmingly positive for the extended sample, where they almost reached statistical significance. These results are in line with what we found in the rest of the paper, however they do not help us reach more robust conclusions on the effect of institutional design on the ``law of $1/n$''.
\end{quote}

\vspace{.3cm}

\noindent \textbf{6)} Reviewer 1 writes: ``The Supplementary Materials is full of content that is of very little use to the reader; even as an online appendix, there is no need to include roughly 100 pages of code from a statistical software. I believe the most relevant Supplementary Materials is the detailed discussion on selection.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that the R script is useful to a limited amount of scholars, and not to the vast majority of readers. As mentioned above, we have separated the Supplementary Materials in two parts. The first follows Reviewer 1's recommendation, including a discussion of the theory, the study selection procedures, a description of how we coded the data in detail, and analysis results. The second gathers all scripts we use in each step of the study, and is aimed at those wishing to replicate our work or to produce new meta-analyses in the social sciences.
\end{quote}

### 2022-11-29 appendix/appendix.Rmd
add paragraph to conclusion

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

@@

This appendix contains the `R` code required to replicate the results we
present in "_Vigilantism and Institutions: Understanding Attitudes towards
Lynching in Brazil_". This file also includes the descriptive statistics of our
sample, the average marginal component effects (AMCEs) for our conjoint
experiment, and additional subgroup analyses for all three experiments.

@@

         household_income = fct_relevel(household_income, "Up to R$1,000",

@@

The age distribution of our sample is shown below. The median age of the survey
respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which
indicates that our sample is older than the Brazilian population (median age $=
33.4$ years old) [@ciafactbook2020].

@@

The next demographic variable we show here is race. According to the [Brazilian
Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4%
as Blacks, and 1,1% as Asians or Indigenous. As we see below, our sample
includes more Whites and fewer individuals who identify as Mixed Race. The
number of Blacks roughly coincide with the population statistics.

@@

In our first experiment, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

\begin{table}[htpb]
\small
\begin{center}
\caption{\textbf{Attributes and Levels}}
\label{tab:categories}
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
\Xhline{2\arrayrulewidth}
\small
Gender of crime perpetrator & Male; female \\ [4pt]
Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
Gender of crime victim & Male; female\\ [4pt]
Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
\Xhline{2\arrayrulewidth}
\end{tabular}
\end{center}
\end{table}

@@

Respondents indicated which profile they preferred for extrajudicial
punishment. Prior to the experiments, they had read the following prompt:

@@

Next, we divide our data according to respondents' level of education. As the
number of interviewees with primary or secondary education is low, we merge
them into a single category, while the other levels (high school, college, and
graduate school) remain the same as in our questionnaire.

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable differences among them.

@@

Respondents who had been victimized in the past 12 months also do not have
different preferences towards lynchings victim profiles. The results are
virtually identical for both groups, as one can see below.

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence for our previous findings and confirm
that respondents select lynching victim profiles according to these two
factors. Criminal characteristics, such as age or race, do not seem to be
particularly relevant, as respondents do not mention them as much. The
following terms are _nenhum_ (none), _contra_ (against), _acho_ (I think),
_casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe these
words correspond to cases where respondents wanted to affirm that they do not
have any preference regarding the lynching profiles, or that they would rather
not have chosen any of the alternatives.

@@

Our second experiment measures the effect of information provision on attitudes
about lynching. In particular, we test whether reminding respondents
about the legal and social consequences of vigilante justice reduces the
subjects' level of support for such practice.

@@

We adhered to the ethical guidelines provided by the Institutional Review Board
at Brown University and APSA's Principles and Guidance. To facilitate
transparency, we comment here on a few aspects of our research design. First,
we worked with the Brown University IRB to reduce the risk of harm for
participants taking the survey. This included consultation with a cultural
expert to inform the phrasing of the survey. Second, respondents received
compensation via Qualtrics, which paid respondents directly after they completed
the questionnaire. Each subject in Qualtrics' online panel received the
equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
not finish the survey will not receive compensation. The compensation is
appropriate for the participant population. As of August 17, 2020, Brazil's
monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
survey takes about 20 minutes to complete and respondents received 2.5 USD,
therefore subjects will receive a monetary compensation that is 6 times higher
than the local minimum wage. Third, we do not see any potential or perceived
conflicts of interest in carrying out this research. We received a grant of
$10,000 to conduct this research from the Centre for the Study of Governance &
Society at King’s College London, which receives support from the Templeton
Foundation. We are aware of no conflicts of interest from either source. All of
the code and data will be made publicly available.

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author: 
  - Danilo Freire[^danilo]
  - David Skarbek[^david]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

[^danilo]: School of Social and Political Sciences, University of Lincoln,
<dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.

[^david]: Department of Political Science, Brown University,
<david_skarbek@brown.edu>, <http://davidskarbek.com>.

@@

This appendix contains the `R` code required to replicate the results we present
in "_Vigilantism and Institutions: Understanding Attitudes towards Lynching in
Brazil_". This file also includes the descriptive statistics of our sample, the
average marginal component effects (AMCEs) for our conjoint experiment, and
additional subgroup analyses for the two experiments included in the main
article.

@@

         household_income = fct_relevel(household_income,
                                        "Up to R$1,000",

@@

The age distribution of our sample is shown below. The median age of the survey
respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which indicates
that our sample is older than the Brazilian population (median age $= 33.4$
years old).

@@

The next demographic variable we show here is race. According to the [Brazilian
Census
Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4%
as Blacks, and 1.1% as Asians or Indigenous. As we see below, our sample
includes more Whites and fewer Mixed-Race individuals. The number of Blacks
roughly coincide with their actual population share.

@@

In our first experiment, we present five pairs of criminal profiles to
respondents. Each profile contains eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

\begin{table}[htpb]
\small
\begin{center}
\caption{\textbf{Attributes and Levels}}
\label{tab:categories}
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
\Xhline{2\arrayrulewidth}
\small
Gender of crime perpetrator & Male; female \\ [4pt]
Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
Gender of crime victim & Male; female\\ [4pt]
Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
Lynching perpetrators & Bystanders; neighbors; family of the victim; gangs; police \\
\Xhline{2\arrayrulewidth}
\end{tabular}
\end{center}
\end{table}

@@

Respondents indicated which profile they preferred for extrajudicial punishment.
Prior to selecting the profiles, respondents were asked to read the following prompt:

@@

Next, we divide our data according to respondents' level of education. As the
number of interviewees with primary or secondary education is low, we merge them
into a single category, while the other levels (high school, college, and
graduate school) remain the same as in our questionnaire. While most results are
similar across all model specifications, we find that respondents with a high
school degree tend to punish Blacks more severely, but participants with a
college degree believe that White criminals should be punished more harshly
instead. The finding deserves attention because it indicates that individuals
with lower levels of education, who are more likely to be Black and Mixed Race
in Brazil, perhaps prefer to punish criminals of own race. The same is true for
Whites, who are usually overrepresented in college education. The differences
are not statistically significant, however, for respondents with university
degrees.

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable differences among them, except
the fact that respondents with lower incomes are more likely to select profiles
that include White criminals.

@@

Respondents who had been victimized in the past 12 months also do not have
different preferences towards lynchings victim profiles. The results are
virtually identical for both groups, as one can see below. The only exception is
that respondents who had not been victimized one year prior to the research are
slightly more likely to support the lynching of White criminals.

@@

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence for our previous findings and confirm
that respondents select lynching victim profiles according to these two
factors. Criminal characteristics, such as age or race, do not seem to be
particularly relevant, as respondents do not mention them as much. Then
respondents mention terms like _nenhum_ (none), _contra_ (against), _acho_ (I
think), _casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe
these words correspond to cases where respondents wanted to affirm that they do
not have any preference regarding the lynching profiles, or that they would
rather not have chosen any of the alternatives.

@@

Our second experiment measures the effect of information provision on attitudes
about lynching. In particular, we test whether reminding respondents
about the legal and social consequences of vigilante justice reduces the
subjects' level of support for such practice.[^carryover-effects]

[^carryover-effects]: To prevent eventual carryover effects caused by the
conjoint, we randomized the order of the conjoint and the information provision
experiments.

@@

We adhered to the ethical guidelines provided by the Institutional Review Board
at Brown University and APSA's Principles and Guidance. To facilitate
transparency, we comment here on a few aspects of our research design. First, we
worked with Brown University's IRB to reduce the risk of harm for participants
taking the survey. This included consultation with a cultural expert to inform
the phrasing of the survey. Second, respondents received compensation via
Qualtrics, which paid respondents directly after they completed the
questionnaire. Each subject in Qualtrics' online panel received the equivalent
of 2.5 USD in Brazilian Reals (local currency). Respondents who did not finish
the survey did not receive compensation. The compensation was appropriate for
the participant population. As of August 17, 2020, Brazil's monthly minimum wage
was BRL 1039, which amounted to 191 US dollars. Assuming 40 working hours per
week, the hourly minimum wage equals 1.19 US dollars. Our survey took about 20
minutes to complete and respondents received 2.5 USD, therefore subjects
received a monetary compensation that was 6 times higher than the local minimum
wage. Third, we do not see any potential or perceived conflicts of interest in
carrying out this research. We received a grant of USD 10,000 to conduct this
research from the Centre for the Study of Governance & Society at King’s College
London, which in turn receives support from the Templeton Foundation. We are not
aware of any conflicts of interest from either source. All of the code and data
used in this article have already been made publicly available.
